Structured Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-10-28 R0V0.tex
Start to write about chordal graphs
Add concepts of tree, leaves and cycles

Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise.

@@

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. Let $k\in\mathbb{N}_{[1,N]}$ be a constant value and $\{1,\ldots,k\}$ be a path. A \emph{chord} of a path is any edge joining two nonconsecutive nodes.

A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$.

>>>>

Let $N>0$ be an integer, a \emph{graph} consists of a set of \emph{nodes} $\mathscr{V}\subset\mathbb{N}_{[1,N]}$ and a set of \emph{edges} $\mathscr{E}\subset\mathscr{V}\times\mathscr{V}$ and it is denoted by the pair $(\mathscr{V},\mathscr{E})=\mathscr{G}$. A node $i\in\mathscr{V}$ is said to be \emph{adjacent} to a node $j\in\mathscr{V}$ if $(i,j)\in\mathscr{E}$, the set of nodes that are adjacent to $j$ is defined as $\mathscr{N}(j)=\{i\in\mathscr{V}:i\neq j,(i,j)\in\mathscr{E}\}$. Given two nodes $i,j\in\mathscr{V}$, and ordered sequence of edges $\left\{(k,k+1)\right\}_{k=i}^{j-1}$ is said to be a \emph{path from the node $i$ to the node $j$}. A path is said to be \emph{cycle} if no edges are repeated and the nodes $i$ and $j-1$  are distinct. A graph is said to be \emph{strongly connected} if, for every two nodes $i,j\in\mathscr{V}$, there exists a path connecting them. It is also said to be \emph{complete} is every node is adjacent to any other node, and it is \emph{incomplete} otherwise. A graph is said to be a \emph{tree} if it is connected and does not contain cycles. A \emph{leaf} is a node that is adjacent to only one node.

@@

Consider the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$ describing the topology of the network~\eqref{eq:general system}. A \emph{clique} $\mathscr{C}\subset\mathscr{V}$ of the graph $\mathscr{G}$ is the maximal set of nodes that induces a complete subgraph on $\mathscr{G}$. A \emph{chord} of a path is any edge joining two nonconsecutive nodes. A graph is said to be \emph{chordal} if every cycle greater than three has a chord. The importance of a graph being chordal is that it has a tree-decomposition into cliques  \cite[Proposition~12.3.11]{Diestel2005}.
